master thesis

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - more data, less 'you's

    One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
      can not take divergece times (branch length) into account. Since there are no development times 
      of species in our case, \colorbox{red}{you} can ignore this. \\
    Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
      predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
      like irreversibility of transitions for dollo parsimony. Again, this problem is irrelevant to 
      the problem at hand, because \colorbox{red}{you} can only work with generalized models in the 
      analysis of the entire Eukaryota tree. \\

@@

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            correct predicted $\sim$ taxa & 117877 & 111466 & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa + depth & 117703 & XXXXX & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa * depth & 117592 & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of cross validation prediction}
        \label{table:Residuals cross validation} 
      \end{table}

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            correct predicted $\sim$ taxa & 117936 & 112242 & 111733 & XXXXX \\
            \hline
            correct predicted $\sim$ taxa + depth & 117776 & XXXXX & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa * depth & XXXXX & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BICs of cross validation prediction}
        \label{table:BIC cross validation} 
      \end{table}

>>>>

    One of the major disadvantages of parsimony methods is that, unlike likelihood approaches, they 
      can not take divergece times (branch length) into account. Since the OTL does not include 
      development times of species, this is irrelevant. \\
    Another problem pointed out by Royer-Carenzi is that parsimony approaches are either based on 
      predefined parameters (generalized parsimony) or on strong and often controversial assumptions, 
      like irreversibility of transitions for dollo parsimony. Again, this problem is unimportant to 
      the problem at hand, because in the analysis of the entire Eukaryota tree only generalized 
      models make sense. \\

@@

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            correct predicted $\sim$ taxa & 117877 & 111466 & 108878 & XXXXX \\
            \hline
            correct predicted $\sim$ taxa + depth & 117703 & 110513 & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa * depth & 117592 & 109827 & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of cross validation prediction}
        \label{table:Residuals cross validation} 
      \end{table}

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            correct predicted $\sim$ taxa & 117936 & 112242 & 111733 & XXXXX \\
            \hline
            correct predicted $\sim$ taxa + depth & 117776 & 111304 & 111273 & XXXXX \\
            \hline
            correct predicted $\sim$ taxa * depth & 117709 & 111262 & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BICs of cross validation prediction}
        \label{table:BIC cross validation} 
      \end{table}
